Multi-channel Kondo model URG

### 2021-11-16 multi-channel-urg.tex
wrote down all explicit effective Hamiltonians for two channel Kondo

\documentclass[10pt]{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
\numberwithin{equation}{section}
\allowdisplaybreaks
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{ebgaramond}
\begin{document}
\title{Multi-channel Kondo model URG}
\author{Abhirup Mukherjee}
\date{\today}
\maketitle
\section{Derivation of URG equations for the multi-channel Kondo model}

@@

	&= \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 \left[s_\text{tot}^- s_\text{tot}^+ \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 H_0 - s_\text{tot}^- s_\text{tot}^+ \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} Z_{1,\text{tot}} H_0\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)}\right]\\

@@

At the last step, we dropped the three-particle scattering terms. If we look at the effective Hamiltonian for a state \(\ket{S_d^z=\frac{1}{2}, s_\text{tot}, s^z_\text{tot}}\), we can replace the following operators with scalars:
\begin{gather}
	\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)} = \gamma_{s_\text{tot}}^{s_\text{tot}^z}\\
	s_\text{tot}^- s_\text{tot}^+ = s_\text{tot}\left(s_\text{tot} + 1\right) - s^z_\text{tot}\left(s^z_\text{tot} + 1\right) = \chi_{s_\text{tot}}^{s_\text{tot}^z}
\end{gather}

@@

	H_\text{eff}\ket{\frac{1}{2}, s_\text{tot}, s^z_\text{tot}}\bra{\frac{1}{2}, s_\text{tot}, s^z_\text{tot}} = H_0 + \frac{J}{2}s^z_\text{tot} + \frac{J^2}{4}\gamma_{s_\text{tot}}^{s_\text{tot}^z}\chi_{s_\text{tot}}^{s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}} H_0 - \frac{\gamma_{s_\text{tot}}^{s_\text{tot}^z}}{\chi_{s_\text{tot}}^{s_\text{tot}^z}} s^-_\text{tot}X^\dagger_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right] 

>>>>

\documentclass[12pt]{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
\numberwithin{equation}{section}
\allowdisplaybreaks
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{ebgaramond}
\begin{document}
\title{Multi-channel Kondo model URG}
\author{Abhirup Mukherjee}
\date{\today}
\maketitle
\section{Derivation of URG equations for the multi-channel Kondo model}

@@

	&= \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 s_\text{tot}^- s_\text{tot}^+ \left[\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 H_0 - \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} Z_{1,\text{tot}} H_0\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)}\right]

@@

At the last step, we dropped the three-particle scattering terms.

The other \(n=2\) term gives
\begin{equation}\begin{aligned}
	&s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}\frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^-\\
	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 s_\text{tot}^+ H_0 \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^- \\
	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 s_\text{tot}^+ H_0 \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}\left(s_\text{tot}^- H_0 + X_\text{1,tot}\right) \\
	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 \left[s_\text{tot}^+ H_0 s_\text{tot}^-\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} H_0 + s_\text{tot}^+ H_0\frac{1}{E_\text{gs} - \frac{J}{2}s_\text{tot}^z}X_\text{1,tot}\right] \\
	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 s_\text{tot}^+ \left(s_\text{tot}^- H_0 + X_\text{1,tot}\right)\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} H_0 \\
	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 \left[s_\text{tot}^+s_\text{tot}^- H_0 \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} H_0\right] \\
	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 s_\text{tot}^+s_\text{tot}^- \left[\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} H_0^2 - \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} Z_{1,\text{tot}} \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} H_0 \right] \\
	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 s_\text{tot}^+s_\text{tot}^- \left[H_0^2 \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} - \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} Z_{1,\text{tot}} H_0 \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} \right]
\end{aligned}\end{equation}

If we look at the effective Hamiltonian for a state \(\ket{S_d^z=\frac{1}{2}, s_\text{tot}, s^z_\text{tot}}\), we can replace the following operators with scalars:
\begin{gather}
	\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)} = \gamma_{s_\text{tot}}^{s_\text{tot}^z},\\
	\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} = \gamma_{s_\text{tot}}^{-s_\text{tot}^z}\\
	s_\text{tot}^- s_\text{tot}^+ = s_\text{tot}\left(s_\text{tot} + 1\right) - s^z_\text{tot}\left(s^z_\text{tot} + 1\right) = \chi_{s_\text{tot}}^{s_\text{tot}^z}\\
	s_\text{tot}^+ s_\text{tot}^- = s_\text{tot}\left(s_\text{tot} + 1\right) - s^z_\text{tot}\left(s^z_\text{tot} - 1\right) = \chi_{s_\text{tot}}^{-s_\text{tot}^z}
\end{gather}
They are not all independent: \(\left(\gamma_{s_\text{tot}}^{s_\text{tot}^z}\right)^{-1} + \left(\gamma_{s_\text{tot}}^{-s_\text{tot}^z}\right)^{-1} =  E_\text{gs} + J, \chi_{s_\text{tot}}^{s_\text{tot}^z} - \chi_{s_\text{tot}}^{-s_\text{tot}^z} = -2 s^z_\text{tot}\).

@@

	H_\text{eff}^{\frac{1}{2}, s_\text{tot}, s^z_\text{tot}} = H_0 + \frac{J}{2}s^z_\text{tot} + \frac{J^2}{4}\gamma_{s_\text{tot}}^{s_\text{tot}^z}\chi_{s_\text{tot}}^{s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}} H_0 - \frac{\gamma_{s_\text{tot}}^{s_\text{tot}^z}}{\chi_{s_\text{tot}}^{s_\text{tot}^z}} s^-_\text{tot}X^\dagger_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right] \\
+ \frac{J^2}{4}\gamma_{s_\text{tot}}^{-s_\text{tot}^z}\chi_{s_\text{tot}}^{-s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}} H_0 + \frac{\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}{\chi_{s_\text{tot}}^{-s_\text{tot}^z}} s^+_\text{tot}X_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right]
For the two channel, we have four possible states in total: \(\left( s_\text{tot}, s_\text{tot}^z \right) = \left\{ (0,0), (1,-1), (1,0), (1,1) \right\} \). The state with \(s_\text{tot}=0\) cannot be acted on by \(s_\text{tot}^\pm\), so the effective Hamiltonian for this step will consist of only the diagonal part:
	H_\text{eff}^{\frac{1}{2}, 0, 0} = H_0 + \frac{J}{2}s^z_\text{tot} = H_0
The factors \(\gamma\) and \(\chi\) for the other states are
	s_\text{tot}, s_\text{tot}^z = && (1,-1), && (1,0), && (1,1)\\
	\gamma_{s_\text{tot}}^{s_\text{tot}^z} = && \frac{1}{E_\text{gs}}, && \frac{1}{E_\text{gs} + J/2}, && -- \\
	\chi_{s_\text{tot}}^{s_\text{tot}^z} = && 2, && 2, && --\\
	\gamma_{s_\text{tot}}^{-s_\text{tot}^z} = && --, && \frac{1}{E_\text{gs} + J/2}, && \frac{1}{E_\text{gs}}\\
	\chi_{s_\text{tot}}^{-s_\text{tot}^z} = && --, && 2, && 2\\
The complete set of effective Hamiltonians for the two-channel Kondo model can now be written down:
	H_\text{eff}^{\frac{1}{2}, 0, 0} &= H_0\\
	H_\text{eff}^{\frac{1}{2}, 1, 1} &= H_0 + \frac{J}{2} + \frac{J^2}{4}\frac{2}{E_\text{gs}}\left[1 + \frac{1}{E_\text{gs}} H_0 + \frac{1}{2 E_\text{gs}} s^+_\text{tot}X_{1,\text{tot}} + \frac{1}{E_\text{gs}^2} H_0^2 - \frac{1}{E_\text{gs}^3} Z_{1,\text{tot}} H_0\right] \\
	H_\text{eff}^{\frac{1}{2}, 1, -1} &= H_0 - \frac{J}{2} + \frac{J^2}{4}\frac{2}{E_\text{gs}}\left[1 + \frac{1}{E_\text{gs}} H_0 - \frac{1}{2 E_\text{gs}} s^-_\text{tot}X^\dagger_{1,\text{tot}} + \frac{1}{E_\text{gs}^2} H_0^2 - \frac{1}{E_\text{gs}^3} Z_{1,\text{tot}} H_0\right] \\
	H_\text{eff}^{\frac{1}{2}, 1, 0} &= H_0 + \frac{J^2}{4}\frac{2}{E_\text{gs} + J/2}\left[1 + \frac{1}{E_\text{gs} + J/2} H_0 + \frac{1}{2 E_\text{gs} + J} \left(s^+_\text{tot}X_{1,\text{tot}} - s^-_\text{tot}X^\dagger_{1,\text{tot}}\right) \right.\\
					 &\left.+ \frac{2}{\left(E_\text{gs} + J/2\right)^2} H_0^2 - \frac{2}{\left(E_\text{gs} + J/2\right)^3} Z_{1,\text{tot}} H_0\right] \\
The terms have the following meanings:
	H_0 &= \sum_{k,\sigma,l}\epsilon_k^l \hat n_{k,\sigma,l}\\
	H_0^2 &= \sum_{k_1,k_2,l_1,l_2,\sigma_1,\sigma_2}\epsilon_k^{l_1}\epsilon_{k_2}^{l_2} \hat n_{k_1,\sigma_1,l_1}\hat n_{k_2,\sigma_2,l_2}\\
	s^+_\text{tot}X_{1,\text{tot}} &= \sum_{k_1,q_1,k_2,q_2,l_1,l_2}c^\dagger_{k_1, \uparrow, l_1}c^\dagger_{q_1, \downarrow, l_1} \left(\epsilon_{k_2}^{l_2} - \epsilon_{q_2}^{l_2}\right) c^\dagger_{k_2, \downarrow, l_2}c_{q_2, \uparrow, l_2}\\
	s^-_\text{tot}X^\dagger_{1,\text{tot}} &= \sum_{k_1,q_1,k_2,q_2,l_1,l_2}c^\dagger_{k_1, \downarrow, l_1}c^\dagger_{q_1, \uparrow, l_1} \left(\epsilon_{k_2}^{l_2} - \epsilon_{q_2}^{l_2}\right) c^\dagger_{q_2, \uparrow, l_2}c_{k_2, \downarrow, l_2}\\
	Z_{1,\text{tot}} H_0 &= \sum_{k_1,q_1,k_2,\sigma_2,l_1,l_2}\left(\epsilon_{k_1}^{l_1} - \epsilon_{q_1}^{l_1}\right) \epsilon_{k_2}^{l_2} \left(c^\dagger_{k_1, \uparrow, l_1}c^\dagger_{q_1, \uparrow, l_1} - c^\dagger_{k_1, \downarrow, l_1}c^\dagger_{q_1, \downarrow, l_1}\right) \hat n_{k_2,\sigma_2,l_2}\\
